---
title: "FAR Functions"
author: "Ankai Xu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FAR Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(readr)
library(dplyr)
library(tidyr)
library(maps)
```

The document introduces the package FarsFunctions. The packages loads and analyzes data from US 
National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS).

## Functions
The package provides the following functions:
`fars_summarize_years()` calculates the number of accidents per month for the particular years
`fars_map_state()` maps the accidents for a given US state and year


## Summarize monthly accidents

`fars_summarize_years()` calculates the number of accidents per month for the particular year(s).

For example, the following command gives the number of accidents per months for year 2013.
```{r}
fars_summarize_years(years = 2013)
```

## Map accidents by State
`fars_map_state()` maps the accidents for a given US state and in a given year.

For example, you can map the road fatality for State X in year 2013 with:
```{r}
fars_map_state(state.num = 10, year = 2013)
```

