---
title: "FAR Functions"
author: "Ankai Hsu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FAR Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The document introduces the package FarsFunctions. The packages loads and analyzes data from US 
National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS).

## Functions
The package provides the following functions:
`fars_summarize_years()` calculates the number of accidents per month for the particular years
`fars_map_state()` maps the accidents for a given US state and year

These functions builds on basic functions to read files, make file names and read years:
`make_filename()` creates the name of the files that holds the data of a year.
`fars_read()` reads a fars file, file name can me provided by make_filename.
`fars_read_years()` reads fars file for multiple years.

## Example: summarize monthly accidents

`fars_summarize_years()` calculates the number of accidents per month for the particular year(s).

For example, the following command gives the number of accidents per months for year 2013.
```{r eval=FALSE}
fars_summarize_years(years=2013)
```

## Example: Map accidents by State
`fars_map_state()` maps the accidents for a given US state and in a given year.


For example, you can map the road fatality for State X in year 2013 with:
```{r eval=FALSE}
fars_map_state(state.num = 10, year = 2013)
```

